Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-07 hpmoon-asoco.tex
More changes by Julio

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{The individual chosen to migrate is selected using Binary Tournament, as it has been previously used by other authors \cite{xiong2003parallel,Xiao03specialized}. As there is not a synchronization step to arrange the individual parts besides the specific crossover and mutation operations, the destination island after migration is chosen randomly to ensure that the modified parts of the migrated individual can be taken into account by the whole set of  islands. Migration is performed asynchronously, as it have the advantage of being a non-blocking operation \cite{TalbiUnified2018}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one run of each combination, also allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark. The first one, ZDT1, has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}. Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is still larger.}

%ZDT2
\textcolor{blue}{ZDT2 has a non-convex Pareto front as it is shown in Figures 7 and 8. From these figures is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.  Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}

%ZDT3
\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations. However, with $L=512$, some of the $A$ configurations skip the last region on the right with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $A$). In the case of $L=2048$, the rightmost part appears in all configurations, and being the Spread metric not significantly different between all the configurations (as shown in Table \ref{tab:results2048}), the HV metric is the only one that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}

@@

This work has been partially funded by projects SPIP2017-02116, EphemeCH TIN2014-56494-C4-3-P, DeepBio TIN2017-85727-C4-2-P and TEC2015-68752.
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

>>>>

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. According to Alba and Luque \cite{EVALUATIONPARALLEL}, other stop criteria such as the number of evaluations required to attain a solution, may be misleading depending on the studied scenario. In our case we have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time. The number of generations between migrations has been set to 5, as this number is usually repeated in the literature \cite{Deb03distributed,Martens13asynchronous}. \textcolor{blue}{Migration is performed asynchronously, as it has the advantage of being a non-blocking operation \cite{TalbiUnified2018}. The individual chosen to migrate is selected using Binary Tournament, as proposed in previous papers  \cite{xiong2003parallel,Xiao03specialized}. Whenever an island starts the migration step, the migrated individual is sent to another randomly selected island. This makes it possible a dissemination of the modified parts of the individuals among the whole set of islands, thus avoiding a specific synchronization step to compose solutions obtained by different islands, as occurs other works \cite{Dorronsoro13superlinear}.}
 The whole parameter set is summarized in Table \ref{tab:parameters}. 
 \textcolor{blue}{It is important to point out that we have carried out experiments modifying only the number of islands and the size of the problem, as other researchers have done \cite{CaoZLL17,Dorronsoro13superlinear,DorronsoroPSO2018,Martens13asynchronous,Durillo08masterslave}, who did not carry out studies on other parameters apart from these. This allows us to focus on the objective of this article, which is to demonstrate that on equal terms, the use of SLA can lead to improved performance depending on the combination of the number of islands and the size of the chromosome.}

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
\textcolor{blue}{Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination. These figures allow to visualize the effect of the different chromosome sizes and number of islands in each different benchmark. The first one, ZDT1, has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown in average in Table \ref{tab:results512}. Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is still larger.}

%ZDT2
\textcolor{blue}{ZDT2 has a non-convex Pareto front. From Figures \cite{fig:plot_zdt2_512} and \cite{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.  Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.}

%ZDT3
\textcolor{blue}{ZDT3 Pareto-optimal front is formed by non-contiguous convex parts, and plots for both chromosome sizes (Figures \ref{fig:plot_zdt3_512} and \ref{fig:plot_zdt3_2048}) show solutions gathered in similar regions in all configurations. However, with $L=512$, the rightmost part of the obtaninde non-dominated solutions is not obtained in the $A$ alternative with $P=8$  and $P=16$ (being equivalent to alternatives $O$ and $D$). This explains why with this chromosome length, the SLA methods not improve the results obtained by $B$. This problem does not appear when $L=2048$. Although the differences in the Spread metric are not significant for the different alternatives for this benchmark, (as shown in Table \ref{tab:results2048}), the HV and IGD metrics are the ones that can be used to show the effectiveness of our approach in this type of problem with non-continuous PFs.}

@@

This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects EphemeCH TIN2014-56494-C4-3-P, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
Econom{\'ia}a y Competitividad'' and ERDF funds).
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.
